A molecular taxonomy of tumors independent of tissue-of-origin

### 2020-08-16 text/fig_legend.Rmd
Fix some bad LaTeX in fig 9 label

**Figure 8** Tissue specific effects are compared by showing the
probability density for the posterior value of the k_tis
multiplier. These values reflect the general deadliness of the cancer
type across all clusters. GBM, PAAD, and SKCM stand out as having
values in the 10 to 20 range with a wide degree of uncertainty. Other
cancers such as Prostate (PRAD) and Thyroid (THCA) show values down
near or even below 1 suggesting that these populations may have
healthier lifestyles and more access to care. Most cancer types fall
in the range 2-7 as might be expected.

**Figure 9** Class specific $k_class$ values shown for each cancer
type. The overall $k$ value is the product of $k_tis \times
k_class$. The class specific value shows the relative aggressiveness
of that particular class within the tissue. For example class 1, 2,
and 6 Glioblastoma (GBM) are apparently much less deadly than other
types of GBM. A similar situation can be seen with Pancreatic Cancer
(PAAD) where 1, 6, and 8 are less deadly compared to classes 7,
9, 10. For some cancer types there are few data points and little
ability to estimate values with precision (DLBC and KICH for example).

>>>>

**Figure 8** Tissue specific effects are compared by showing the probability
density for the posterior value of the $k_{tis}$ multiplier. These values
reflect the general deadliness of the cancer type across all clusters. GBM,
PAAD, and SKCM stand out as having values in the 10 to 20 range with a wide
degree of uncertainty. Other cancers such as Prostate (PRAD) and Thyroid (THCA)
show values down near or even below 1 suggesting that these populations may have
healthier lifestyles and more access to care. Most cancer types fall in the
range 2-7 as might be expected.

**Figure 9** Class specific $k_{class}$ values shown for each cancer type. The
overall $k$ value is the product of $k_{tis} \times k_{class}$. The class
specific value shows the relative aggressiveness of that particular class within
the tissue. For example class 1, 2, and 6 Glioblastoma (GBM) are apparently much
less deadly than other types of GBM. A similar situation can be seen with
Pancreatic Cancer (PAAD) where 1, 6, and 8 are less deadly compared to classes
7, 9, 10. For some cancer types there are few data points and little ability to
estimate values with precision (DLBC and KICH for example).
